---
title: "Regression and Statistical Inference"
format:
  html:
    self-contained: false
toc: true
theme: "cosmo"
---


# Read data
```{r}
#| output: asis
# Load the Library

library(dplyr)
library(tidyverse)

# Load the Data & Check Dimension
car_prices <- readRDS("E:/Master Study/TUHH/Wise 23-24/Causal Data Science for Business Analytics/Causal_Data_Science_Data/car_prices.rds")
head(car_prices)
dim(car_prices)
```

# data types do you see? How do numbers differ from strings regarding their data type?
```{r}
#| output: asis
car_prices <- readRDS("E:/Master Study/TUHH/Wise 23-24/Causal Data Science for Business Analytics/Causal_Data_Science_Data/car_prices.rds")
head(car_prices)
str(car_prices)

print("Numbers are described by 'num', while strings are described by 'chr'. In this dataset, another data type is also exist, which is boolean described by 'logic'")
```

# Run a linear regression. You want to explain what factors are relevant for the pricing of a car.
```{r}
#| output: asis

# Include all potential regressors
lm_all <- lm(price ~ ., data = car_prices)
summary(lm_all)
```

# 	Choose one regressor (Data type, Effect of changing value to the price, whether it is statistically significant
```{r}
#| output: asis

print("One regressor chosen is peakrpm. It has decimal (numbers) data type. Its effect on the price can be shown by its slope (coefficient).
      For 1 peak rpm higher, it increases the price by 2.536 unit price. The peak rpm effect on price is statistically significant, indicated by p-value much lower than <0.05.
      The p-value of peak rpm is 0.000108, which means it has highly significant effect on price.")
```

#  Add a variable seat_heating to the data and assign a value TRUE for all observations. What coefficient do you get for the new variable seat_heating and how can you explain it?
```{r}
#| output: asis

car_prices <- car_prices %>%
  mutate(seat_heating = TRUE)

lm_all <- lm(price ~ ., data = car_prices)
summary(lm_all)
lm_seatheating <- lm(price ~ seat_heating, data = car_prices)
summary(lm_seatheating)

print ("Coefficient on seat heating is not available since all cars have seat heating but it doesn't increase the price.
       Mathematically, changes in price (as Y axis), but no changes in seat heating (as X axis) would result delta Y/ delta X not available N/A since
       any numbers divided by 0 is undefined.")
```